Pricing Parisian options under a Gaussian process

### 2017-04-28 Pricing Parisian options under a Gaussian process.tex
20170428

\documentclass{ctexart} % Default font size is 12pt, it can be changed here
\ctexset{section/format = {\Large\bfseries}}
\usepackage{geometry} % Required to change the page size to A4
\geometry{a4paper} % Set the page size to be A4 as opposed to the default US Letter
\geometry{left=1.6cm,right=1.6cm,top=3.5cm,bottom=3.5cm}
%\usepacjage{subfigure}
\usepackage{graphicx} % Required for including pictures
\usepackage{amsmath}
\usepackage{amssymb,bm}
%\usepackage{abstract}
\usepackage{float} % Allows putting an [H] in \begin{figure} to specify the exact location of the figure
%\usepacjage{wrapfig} % Allows in-line images such as the example fish picture

%\linespread{1.2} % Line spacing

%\setlength\parindent{0pt} % Uncomment to remove all indentation from paragraphs
\usepackage{enumerate}
\graphicspath{{Pictures/}} % Specifies the directory where pictures are stored

\newtheorem{definition}{\hspace{2em}定义}[section] % 如果没有章, 只有节, 把上面的[chapter]改成[section] 
\newtheorem{theorem}[definition]{\hspace{2em}定理} 
\newtheorem{axiom}[definition]{\hspace{2em}公理} 
\newtheorem{lemma}[definition]{\hspace{2em}引理} 
\newtheorem{proposition}[definition]{\hspace{2em}命题} 
\newtheorem{corollary}[definition]{\hspace{2em}推论} 
\newtheorem{remark}{\hspace{2em}注}[section] %类似地定义其他“题头”. 这里“注”的编号与定义、定理等是分开的

@@

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thicjness here

\center % Center everything on the page
%%\includegraphics[width=2.5cm]{Pictures/SCE.png}
%%\textsc{\LARGE University Name}\\[1.5cm] % Name of your university/college
%%\textsc{\Large Maior Heading}\\[0.5cm] % Maior heading such as course name
%%\textsc{\large Minor Heading}\\[0.5cm] % Minor heading such as course title

\HRule \\[0.4cm]
{ \huge \bfseries Pricing Parisian options under a Gaussian process}\\[0.4cm] % Title of your document
\HRule \\[1.5cm]

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
Ming \textsc{Li} % Your name
\end{flushleft}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Department:} \\
Mathematics
\end{flushright}
\end{minipage}\\[4cm]

{\large \today}\\[3cm] % Date, change the \today to a set date if you want to be precise

%\includegraphics{Logo}\\[1cm] % Include a department/university logo - this will require the graphicx pacjage

\vfill % Fill the rest of the page with whitespace
\end{titlepage}
\newpage
%\begin{abstract}
This study extends the Parisian option pricing model to general Gaussian processes to adapt more asset pricing model assumptions. This study uses a Wick-Ito integral to derive the consecutive and cumulative Parisian option pricing PDEs under Gaussian processes and construct an unconditionally stable implicit difference scheme. Additionally, a numerical method with efficient computation, namely, a chasing algorithm, is used to solve the pricing problem. When analysing the example of the price of consecutive and cumulative Parisian options under any Gaussian process, because the counter is not zero, the cumulative Parisian option is more likely a knock-out option, and the price is lower than that of the consecutive Parisian option. The variables that affect the prices of the Parisian option under a Gaussian process are a slow-growing variance function, smaller volatility, more likely profit and loss forecasts, steeper graph of the price of the Parisian option, and higher peak value.

{\bf Key Words: }Parisian Option, Gaussian Process, Chasing Algorithm, Brownian Motion, Implicit Difference Equations
%\end{abstract}

@@

\section{Gaussian Process}
The financial market is a complex system, and most investors do not have access to adequate information. Investors gain profits while taking risks. In the efficient market hypothesis, noise is defined as the deviation between the price and the value of financial assets. Most investors are noise traders: they normally treat noise information as factual information to trade. Information traders use noise-trader-characteristics to make profits due to a herd mentality. This introduces market excess and volatility, which leads to market volatility clustering. Similar yields on different time scales with similar distributions of frequency, such as auto-correlation in time scales, results from new investors who take the same risk level as a crowd of investors. Financial markets have a long memory, which includes past information that not only affects current markets but also affects future markets.\\

@@

If $F(t,s)=t\wedge s$, then $W_t$ is a standard Brownian motion. If $F(t,s)=1/2(t^{2H}+s^{2H}-|t-s|^{2H})$, then $W_t$  is a fractional Brownian motion with Hurst number H. When $H\in(0,1/2)$, increments are negatively correlated, $W_t$has a short-term dependence and anti-persistence, and its future growth does not follow past trends. When $H\in(1/2,1)$, $W_t$  has a long-term dependence and persistence and future trends will be extended by past growth trends.\\

The covariance function of a bi-fractional process is F$F(t,s)=1/2^K[(t^{2H}+s^{2H})^K-|t-s|^{2HK}]$. It has properties such as auto-correlation and long-memory of fractional process, and when $2HK=1$, $W_t$ is a semi-martingale.\\
The sub-fractional process also has auto-correlation and long-memory properties, but it has a faster degradation speed than does fractional Brownian motion. Its covariance function is $F(t,s)=t^{2H}+s^{2H}-1/2(|t+s|^{2H}+|t-s|^{2H})$.\\

Mixed fractional Brownian motion is a linear combination of standard Brownian motion and fractional Brownian motion. Suppose$B_t$ is a Brownian motion and $B_t^H$ is a fractional Brownian motion; then, $W_t=\alpha B_t+\beta B_t^H$, where $\alpha,\beta \in R$ and its covariance function is  $F(t,s)=\alpha^2(t\wedge s)+\beta(t^{2H}+s^{2H}-|t-s|^{2H})/2$ 
%We express $F(t,t)=F_t$，$dF_t/dt=U_t$ and provide a summary of each motion in Table \ref{tabl1}：
\begin{table}[htbp]
\centering
\caption{各种高斯过程的协方差函数}
\label{tabl1}
\begin{tabular}{ccc}
\hline
高斯过程& $F_t$ & $U_t$ \\
\hline
布朗运动 & $t$ & $1$ \\
分数布朗运动 & $t^{2H}$ & $2Ht^{2H-1}$ \\
双分数布朗运动 & $t^{2HK}$ & $2HKt^{2HK-1}$ \\
次分数布朗运动 & $(2-2^{2H-1})t^{2H}$ & $(4-2^{2H})Ht^{2H-1}$ \\
混合分数布朗运动 & $\alpha^2t+\beta^2t^{2H}$ & $\alpha^2+2H\beta^2t^{2H-1}$ \\
\hline
\end{tabular}
\end{table}

本文主要研究在一般的高斯过程下连续型和累计型巴黎期权的偏微分方程，并通过构造差分方程进行求解。最后选择不同$U_t$的高斯过程，通过算例求解，讨论各个模型参数对连续型和累计型巴黎期权价格的影响。以及两种类型巴黎期权的比较。

\section{Wick-Ito 积分}
当高斯过程$W_t$既不是Markovian过程，也不是半鞅时，Rogers证明了按照路径型积分建立的金融市场数学模型存在套利机会。而在一个存在套利机会的市场中对金融衍生品定价是不切实际的。因此，本文使用如下的Wick-Ito积分
\begin{equation}
\int_a^bf(t,\omega)dW_t=\lim_{\| \Pi\| \rightarrow0}\sum^{n-1}_{k=0}f(t_k,\omega)\diamond (W_{t+1}-W_t)
\end{equation}
其中$\diamond$代表Wick乘积。由此定义的随机积分宽假下，金融市场数学模型是无套利的并且市场是完备的。

下面引入关于高斯过程的Wick-Ito公式，其证明过程请参考文献\cite{ref16}
\begin{lemma}
\label{x1}
设$Y_t$是一方差有界的中心型高斯变量，记$F_t=E(Y^2_t)$，函数$f(t,y):[0,+\infty]\times R\rightarrow R$是连续的，其偏导数$\frac{\partial f}{\partial t}$，$\frac{\partial f}{\partial y}$，$\frac{\partial^2 f}{\partial y^2}$均存在且满足指数型增长条件，即$\forall t\in[0,T]$，$x \in R$有
\begin{equation}
|\frac{\partial^k f(t,y)}{\partial y^k}|\leq C_T\exp(c_Ty^2),\quad k=0,1,2
\end{equation}
则Wick-Ito公式的积分形式为
\begin{equation}
f(T,Y_T)=f(0,Y_0)+\int^T_0\frac{\partial f}{\partial y}(t,Y_t)dt+\int^T_0\frac{\partial f}{\partial y}(t,Y_t)\diamond dY_t+\frac{1}{2}\frac{\partial^2 f}{\partial y^2}(t,Y_t)dF_t
\end{equation}
其中，$C_T$，$c_T$均大于零的常数，且满足$c_T<\frac{1}{4}\sup_{t\in[0,T]}F_t^{-1}$，$\diamond$表示Wick乘积，同时Wick-Ito公式的微分形式为
\begin{equation}
df(T,Y_T)=f(0,Y_0)+\int^T_0\frac{\partial f}{\partial y}(t,Y_t)dt+\frac{\partial f}{\partial y}(t,Y_t)\diamond dY_t+\frac{1}{2}\frac{\partial^2 f}{\partial y^2}(t,Y_t)dF_t
\end{equation}
\end{lemma}

由引理\ref{x1}，我们可以得到以下定理\cite{ref16}
\begin{theorem}
设$W_t$为一方差有界的高斯过程，标的资产$S_t$为一随机过程且满足
\begin{equation}
dS_t=\mu S_tdt+\sigma S_t\diamond dW_t
\end{equation}
$V(S_t,t)$为一关于$S_t$的金融衍生品的价格，$r$为无风险利率，$F(t)=E(W^2_t)$，$U_t=\frac{dF(t)}{dt}$则任意时刻$t\in[0,T]$，$V(S_t,t)$满足偏微分方程
\begin{equation}
\label{f1}
\frac{\partial V}{\partial t}+\frac{1}{2}\sigma^2S^2U_t\frac{\partial V}{\partial S^2}+\mu S\frac{\partial V}{\partial t}=rV
\end{equation}

\end{theorem}

\section{高斯运动下巴黎期权定价模型}
设$S(t)$为一个公司股票的价格过程，满足下列随机微分方程
\begin{equation}
dS_t=(r-q)S_t dt+\sigma S_t \diamond dW_t
\end{equation}
其中$r$为无风险利率，$\sigma^2$为股票价格波动率方差。$W_t$为一高斯过程，$F_t=E(W^2_t)$，$dF_t/dt=U_t$。
\subsection{连续型向上敲出看涨巴黎期权}
考虑向上敲出看涨欧式巴黎期权(Up-and-Out Call)的定价问题。$J$表示股票价格$S_t$在障碍水平$L$之上连续时间的长度，定义为
\begin{equation}
J(t)=t-\sup(t'\leq t|S_t'\leq D)
\end{equation}
于是有
\begin{equation}
dJ(t)=\left\{
\begin{aligned}
&dt,\quad &S_t>L \\
&-J(t_-),\quad&S_t=L\\
&0,\quad&S_t<L&
\end{aligned}
\right.
\end{equation}
巴黎期权的价格$V$是标的资产价格$S$，时间$t$及资产价格连续超过障碍的时间当前计数值$J$的函数，记为$V(S,J,t)$。假定障碍价格$L>E$，根据动态复制的理论，结合方程\ref{f1}，向上敲出看涨的巴黎期权的价格应满足方程
\begin{equation}
\label{eq}
\frac{\partial V}{\partial t}+H(S-L)\frac{\partial V}{\partial J}+(r-q)S\frac{\partial V}{\partial S}+\frac{1}{2}\sigma^2S^2U\frac{\partial^2 V}{\partial S^2}-rV=0
\end{equation}
求解区间为$0\leq J \leq D$，$0\leq t \leq T$，$0< S < \infty$，其中函数
\begin{equation}
H(x)=\left\{
\begin{aligned}
1 \quad x>0 \\
0 \quad x\leq 0
\end{aligned}
\right.
\end{equation}
根据巴黎期权的定义，当标的资产价格连续超过障碍$L$的时间达到$D$时(即$J=D$时)即敲出，其价值为零。
\begin{equation}
V(S,t,D)=0
\end{equation}
每当发生$S<L$时，$J$重置为零。当$J=0$时，考虑$V$在$J=0$处的连续性，定解条件为
\begin{equation}
\label{bc1}
V(L,t,J)=V(L,t,0)
\end{equation}
当$t=T$时，期权没有敲出，执行期权的终端支付，即满足
\begin{equation}
V(S,T,J)=(S-E)^{+} 
\end{equation}
由于当$S<L$时，$J$恒为$0$，因此可以简记为$V(S,t)$，满足
\begin{equation}
\label{down}
\frac{\partial V}{\partial t}+(r-q)S\frac{\partial V}{\partial S}+\frac{1}{2}\sigma^2S^2U_t\frac{\partial^2 V}{\partial S^2}-rV=0
\end{equation}
当$S>L$，$0<J<D$时,$V(S,t,J)$满足
\begin{equation}
\label{up}
\frac{\partial V}{\partial t}+\frac{\partial V}{\partial J}+(r-q)S\frac{\partial V}{\partial S}+\frac{1}{2}\sigma^2S^2U_t\frac{\partial^2 V}{\partial S^2}-rV=0
\end{equation}
\subsection{累计型向上敲出看涨巴黎期权}
在累计时间下，在$S<L$时，计时器$J$不清零也不计时，其微分表达式为
\begin{equation}
dJ(t)=\left\{
\begin{aligned}
&dt,\quad &S_t\geq L \\
&0,\quad&S_t<L&
\end{aligned}
\right.
\end{equation}
累计型向上敲出看涨巴黎期权的价值同样满足方程\eqref{eq}，但是由于$J$不重置，其定解条件不包含\eqref{bc1}
\begin{equation}
\label{bc2}
\left\{
\begin{aligned}
V(S,T,J)&=(S-E)^{+} \\
V(S,t,D)&=0
\end{aligned}
\right.
\end{equation}

\section{数值求解}
离散化方程\eqref{down}与\eqref{up}，令$S_i=S_0+i\Delta h$，$i\in[0,M]$，$S_{I}=L$；$t_n=n\Delta t$，$n\in[0,N]$，$N\Delta t=T$；$J_j=j\Delta t,j\in[0,K]$，$K\Delta t=D$。

当$S<L$时，构造差分格式
\begin{equation}
\frac{V^{n+1}_i-V^n_i}{\Delta t}+(r-q)S_i\frac{V^{n}_{i+1}-V^{n}_{i-1}}{2\Delta h}+\frac{1}{2}\sigma^2S_i^2U_{n}\frac{V_{i+1}^{n}-2V_i^{n}+V_{i-1}^{n}}{\Delta h^2}-rV^{n}_i=0
\end{equation}
即
\begin{equation}
\label{hcon1}
V^{n}_i-(a^n_iV^{n}_{i-1}+b^n_iV^{n}_i+c^n_iV^{n}_{i+1})=V^{n+1}_i
\end{equation}
其中
$$
a^n_i=-\frac{(r-q)S_i\Delta t}{2\Delta h}+\frac{\sigma^2S_i^2U_{n}\Delta t}{2\Delta h^2},\quad b^n_i=-r\Delta t-\frac{\sigma^2S_i^2U_{n}\Delta t}{\Delta h^2},\quad c^n_i=\frac{(r-q)S_i\Delta t}{2\Delta h}+\frac{\sigma^2S_i^2U_{n}\Delta t}{2\Delta h^2}
$$

当$S>L$时，构造差分格式
\begin{equation}
\frac{V^{n+1}_{i,j+1}-V^{n}_{i,j}}{\Delta t}+(r-q)S_i\frac{V^{n}_{i+1,j}-V^{n}_{i-1,j}}{2\Delta h}+\frac{1}{2}\sigma^2S_i^2U_{n}\frac{V_{i+1,j}^{n}-2V_{i,j}^{n}+V_{i-1,j}^{n}}{\Delta h^2}-rV^{n}_{i,j}=0
\end{equation}
即
\begin{equation}
\label{hcon2}
V^n_{i,j}-(a^n_iV^{n}_{i-1,j}+b^n_iV^{n}_{i,j}+c^n_iV^{n}_{i+1,j})=V^{n+1}_{i,j+1}
\end{equation}

当$S=L$时，综合\eqref{hcon1}和\eqref{hcon2}以及定解条件\eqref{bc1}，需满足
\begin{equation}
V^n_{I}-(a^n_IV^{n}_{I-1}+b^n_IV^{n}_{I}+c^n_IV^{n}_{I+1,0})=V^{n+1}_{I}
\end{equation}
\begin{equation}
V^{n}_{I+1,0}-(a^n_IV^{n}_{I}+b^n_IV^{n}_{I+1,0}+c^n_IV^{n}_{I+2,0})=V^{n+1}_{I+1,1}
\end{equation}

在两端，使用如下线性近似
\begin{equation}
(1-2a^n_0-b^n_0)V^n_0+(a^n_0-c^n_0)V^{n}_{1}=V^{n+1}_0
\end{equation}
\begin{equation}
(1-2c^n_M-b^n_M)V^n_{M,j}+(c^n_M-a^n_M)V^{n}_{M-1,j}=V^{n+1}_{M,j+1}
\end{equation}

终端函数为
\begin{equation}
\label{hb}
V_{i,j}^N=(S_i-E)^+,\quad V_{i,K}^n=0
\end{equation}

方程\eqref{hcon1}和\eqref{hcon2}可写成矩阵形式
\begin{equation}
\label{meq1}
\left(
\begin{matrix}
1-2a^n_0-b^n_0 & a^n_0-c^n_0 & 0       &\ldots  & \ldots &\ldots     & 0 \\
-a^n_1       & 1-b^n_1   & -c^n_1    &\ldots  & \ldots &\ldots     & 0       \\
\vdots     & \ddots  & \ddots  &\ddots  & \vdots & \vdots   & \vdots   \\
0          & \ldots  & -a^n_I    & 1-b^n_I  & -c^n_I    & \ldots  & 0    \\
\vdots     & \vdots  & \vdots  &\ddots  & \ddots & \ddots   & \vdots   \\
0          & \ldots  & \ldots  &\ldots  & a^n_{M-1} & 1-b^n_{M-1} & -c^n_{M-1}   \\
0          & \ldots  & \ldots  &\ldots  &0        & c^n_M-a^n_M & 1-2c^n_M-b^n_M      
\end{matrix}
\right)
\left(
\begin{matrix}
V_0^n\\
V_1^n\\
\vdots\\
V_I^n\\
\vdots\\
V_{M-1,0}^n\\
V_{M,0}^n
\end{matrix}
\right)
=
\left(
\begin{matrix}
V_0^{n+1}\\
V_1^{n+1}\\
\vdots\\
V_I^{n+1}\\
\vdots\\
V_{M-1,1}^{n+1}\\
V_{M,1}^{n+1}
\end{matrix}
\right)
\end{equation}
以及
\begin{equation}
\label{meq2}
\left(
\begin{matrix}
1          & 0       & 0       &\ldots  & \ldots &\ldots     & 0 \\
-a^n_I       & 1-b^n_I   & -c^n_I    &\ldots  & \ldots &\ldots     & 0       \\
\vdots     & \ddots  & \ddots  &\ddots  & \vdots & \vdots    & \vdots   \\
0          & \ldots  & \ldots  &\ldots  & a^n_{M-1} & 1-b^n_{M-1} & -c^n_{M-1}   \\
0          & \ldots  & \ldots  &\ldots  &0        & c^n_M-a^n_M   & 1-2c^n_M-b^n_M      
\end{matrix}
\right)
\left(
\begin{matrix}
V_I^n\\
V_{I+1,j}^{n}\\
\vdots\\
V_{M-1,j}^{n}\\
V_{M,j}^{n}
\end{matrix}
\right)
=
\left(
\begin{matrix}
V_I^n\\
V_{I+1,j+1}^{n+1}\\
\vdots\\
V_{M-1,j+1}^{n+1}\\
V_{M,j+1}^{n+1}
\end{matrix}
\right)
\end{equation}

>>>>

%% This is file `elsarticle-template-1-num.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%%
%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
%%
\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath}
\usepackage{amssymb,bm}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}
\newtheorem{definition}{\hspace{2em} Definition}[section] 
\newtheorem{theorem}[definition]{\hspace{2em}Theorem} 
\newtheorem{axiom}[definition]{\hspace{2em}Axiom} 
\newtheorem{lemma}[definition]{\hspace{2em}Lemma} 
\newtheorem{proposition}[definition]{\hspace{2em}Proposition} 
\newtheorem{corollary}[definition]{\hspace{2em}Corollary} 
\newtheorem{remark}{\hspace{2em}Remark}[section] 
%\journal{Nuclear Physics B}

@@

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Pricing Parisian options under a Gaussian process}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author{Han Yu}

\address{}

\begin{abstract}
This study extends the Parisian option pricing model to general Gaussian processes to adapt more asset pricing model assumptions. This study uses a Wick-Ito integral to derive the consecutive and cumulative Parisian option pricing PDEs under Gaussian processes and construct an unconditionally stable implicit difference scheme. Additionally, a numerical method with efficient computation, namely, a chasing algorithm, is used to solve the pricing problem. When analysing the example of the price of consecutive and cumulative Parisian options under any Gaussian process, because the counter is not zero, the cumulative Parisian option is more likely a knock-out option, and the price is lower than that of the consecutive Parisian option. The variables that affect the prices of the Parisian option under a Gaussian process are a slow-growing variance function, smaller volatility, more likely profit and loss forecasts, steeper graph of the price of the Parisian option, and higher peak value.
\end{abstract}

\begin{keyword}
Parisian Option, Gaussian Process, Chasing Algorithm, Brownian Motion, Implicit Difference Equations
\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

%% main text

@@

\section{Gaussian Process}
The financial market is a complex system, and most investors do not have access to adequate information. Investors gain profits while taking risks. In the efficient market hypothesis, noise is defined as the deviation between the price and the value of financial assets. Most investors are noise traders: they normally treat noise information as factual information to trade. Information traders use noise-trader-characteristics to make profits due to a herd mentality. This introduces market excess and volatility, which leads to market volatility clustering. Similar yields on different time scales with similar distributions of frequency, such as auto-correlation in time scales, results from new investors who take the same risk level as a crowd of investors. Financial markets have a long memory, which includes past information that not only affects current markets but also affects future markets.

@@

If $F(t,s)=t\wedge s$, then $W_t$ is a standard Brownian motion. If $F(t,s)=1/2(t^{2H}+s^{2H}-|t-s|^{2H})$, then $W_t$  is a fractional Brownian motion with Hurst number H. When $H\in(0,1/2)$, increments are negatively correlated, $W_t$has a short-term dependence and anti-persistence, and its future growth does not follow past trends. When $H\in(1/2,1)$, $W_t$  has a long-term dependence and persistence and future trends will be extended by past growth trends.\\
The covariance function of a bi-fractional process is F$F(t,s)=1/2^K[(t^{2H}+s^{2H})^K-|t-s|^{2HK}]$. It has properties such as auto-correlation and long-memory of fractional process, and when $2HK=1$, $W_t$ is a semi-martingale.\\
The sub-fractional process also has auto-correlation and long-memory properties, but it has a faster degradation speed than does fractional Brownian motion. Its covariance function is $F(t,s)=t^{2H}+s^{2H}-1/2(|t+s|^{2H}+|t-s|^{2H})$.\\
Mixed fractional Brownian motion is a linear combination of standard Brownian motion and fractional Brownian motion. Suppose$B_t$ is a Brownian motion and $B_t^H$ is a fractional Brownian motion; then, $W_t=\alpha B_t+\beta B_t^H$, where $\alpha,\beta \in R$ and its covariance function is  $F(t,s)=\alpha^2(t\wedge s)+\beta(t^{2H}+s^{2H}-|t-s|^{2H})/2$ 
We express $F(t,t)=F_t$，$dF_t/dt=U_t$ and provide a summary of each motion in Table \ref{tabl1}：

\begin{table}[htbp]
\centering
\caption{Covariance function of different Brownian motion}
\label{tabl1}
\begin{tabular}{ccc}
\hline
Brownian motion& $F_t$ & $U_t$ \\
\hline
Standard Brownian motion & $t$ & $1$ \\
Fractional Brownian motion& $t^{2H}$ & $2Ht^{2H-1}$ \\
Bi-fractional Brownian motion & $t^{2HK}$ & $2HKt^{2HK-1}$ \\
Sub-fractional Brownian motion & $(2-2^{2H-1})t^{2H}$ & $(4-2^{2H})Ht^{2H-1}$ \\
Mixed fractional Brownian motion & $\alpha^2t+\beta^2t^{2H}$ & $\alpha^2+2H\beta^2t^{2H-1}$ \\
\hline
\end{tabular}
\end{table}

\section{Wick-Ito Integral}
When the Gaussian process $W_t$ is neither Markovian nor semi-martingale, Rogers (1997) proved that a path-dependent integral of a financial mathematical model has an arbitrage opportunity. Pricing financial derivatives in a financial market with arbitrage opportunity is unrealistic. Therefore, we use the Wick-Ito integral as follows:
\begin{equation}
\int_a^bf(t,\omega)dW_t=\lim_{\| \Pi\| \rightarrow0}\sum^{n-1}_{k=0}f(t_k,\omega)\diamond (W_{t+1}-W_t)
\end{equation}
where $\diamond$ is a Wick product. Under such a stochastic integral framework, our financial market is complete and has no arbitrage opportunity.
Next, we introduce the Wick-Ito formula into the Gaussian process; for a detailed proof, see Nualart and Taqqu (2008).

\begin{lemma}
\label{x1}
Suppose that $Y_t$ is the bounded variation of a Gaussian variable, denoted by $F_t=E(Y^2_t)$, There is a class of functions $f(t,y):[0,+\infty]\times R\rightarrow R$ whose partial derivatives $\frac{\partial f}{\partial t}$,$\frac{\partial f}{\partial y}$,$\frac{\partial^2 f}{\partial y^2}$ exist and, together with $f$, are continuous and satisfy the following exponential growth condition:
\begin{equation}
|\frac{\partial^k f(t,y)}{\partial y^k}|\leq C_T\exp(c_Ty^2),\quad k=0,1,2
\end{equation}
$\forall t\in[0,T]$,$x \in R$,where $C_T,c_T>0$,and satisfy $c_T<\frac{1}{4}\sup_{t\in[0,T]}F_t^{-1}$T
The integration form of the Wick-Ito formula is expressed by the following:
\begin{equation}
f(T,Y_T)=f(0,Y_0)+\int^T_0\frac{\partial f}{\partial y}(t,Y_t)dt+\int^T_0\frac{\partial f}{\partial y}(t,Y_t)\diamond dY_t+\frac{1}{2}\frac{\partial^2 f}{\partial y^2}(t,Y_t)dF_t
\end{equation}
The differentiation form of Wick-Ito formula is:
\begin{equation}
df(T,Y_T)=f(0,Y_0)+\int^T_0\frac{\partial f}{\partial y}(t,Y_t)dt+\frac{\partial f}{\partial y}(t,Y_t)\diamond dY_t+\frac{1}{2}\frac{\partial^2 f}{\partial y^2}(t,Y_t)dF_t
\end{equation}
\end{lemma}
From Lemma \ref(x1), we can obtain the following theorem:
Theorem 3.2 Suppose that $W_t$ is a Gaussian process with bounded variation; the underlying asset $S_t$ is a stochastic process and satisfies:
\begin{equation}
dS_t=\mu S_tdt+\sigma S_t\diamond dW_t
\end{equation}
$V(S_t,t)$  is a financial derivative of $S_t$ that denotes price, $r$ is the risk-free rate, $\sigma$ is the volatility of the stock price, and the Gaussian process is $W_t$. Let $F(t)=E(W^2_t)$，$U_t=\frac{dF(t)}{dt}$. At any time $t\in [0,T]$, $V(S_t,t)$ satisfies the following partial differential equation:
\begin{equation}
\label{f1}
\frac{\partial V}{\partial t}+\frac{1}{2}\sigma^2S^2U_t\frac{\partial V}{\partial S^2}+\mu S\frac{\partial V}{\partial t}=rV
\end{equation}                 
\section{Pricing Parisian Option under Gaussian Process}
Suppose that $S_t$ is a process of stock price and satisfies the following equation:
\begin{equation}
dS_t=(r-q)S_t dt+\sigma S_t \diamond dW_t
\end{equation}
where $r$ is a riskless interest rate and $\sigma$ is the volatility of stock price. $W_t$ is a Gaussian process such that $F_t=E(W_t^2 )$ and $U_t=(dF_t)/dt$.
\subsection{Consecutive Parisian Option}
First, we consider the pricing up-and-out call of the consecutive Parisian option. $J$ is the continuous time length where the stock price $S_t$  is above the barrier level $L$ and is expressed by
\begin{equation}
J(t)=t-\sup(t'\leq t|S_t'\leq D)
\end{equation}
Then,	
\begin{equation}
dJ(t)=\left\{
\begin{aligned}
&dt,\quad &S_t>L \\
&-J(t_-),\quad&S_t=L\\
&0,\quad&S_t<L&
\end{aligned}
\right.
\end{equation}
The price of the Parisian option $V$ is a function of asset price $S$, time $t$ and the current numerically valued asset price over barriers in continuous time $J$, denoted by $V=V(S,J,t)$. Let the barrier price be $L>E$; according to the theory of dynamic replication and combing with equation (6), the up-and-out call of the Parisian option satisfies the following PDE:
\begin{equation}
\label{eq}
\frac{\partial V}{\partial t}+H(S-L)\frac{\partial V}{\partial J}+(r-q)S\frac{\partial V}{\partial S}+\frac{1}{2}\sigma^2S^2U\frac{\partial^2 V}{\partial S^2}-rV=0
\end{equation}
The intervals that satisfy (10) are $0≤J≤D$,$0≤t≤T$, $0<S<\infty$, and 
\begin{equation}
H(x)=\left\{
\begin{aligned}
1 \quad x>0 \\
0 \quad x\leq 0
\end{aligned}
\right.
\end{equation}
Per the definition of a Parisian option, a knock-out option is the price of an underlying asset over barrier L and the time reached $D$ (as $J=D$), and the value is 0. 
$$V(S,t,D)=0$$
Whenever there are $S<L$, $J$ resets to 0. When $J=0$, consider the continuity of $V$, the definite condition is as follows:
$$V(L,t,J)=V(L,t,0)$$
When t=T, the option did not knock-out, and we exercise the option’s terminal payoff, which satisfies:
$$V(S,T,J)=(S-E)^+$$
When $S<L$, $J=0$, then the option can be denoted by $V(S,t)$  and satisfies the following PDE:
\begin{equation}
\label{down}
\frac{\partial V}{\partial t}+(r-q)S\frac{\partial V}{\partial S}+\frac{1}{2}\sigma^2S^2U_t\frac{\partial^2 V}{\partial S^2}-rV=0
\end{equation}
When $S>L$,$0<J<D$, $V(S,t,J)$, it satisfies the following PDE:
\begin{equation}
\label{up}
\frac{\partial V}{\partial t}+\frac{\partial V}{\partial J}+(r-q)S\frac{\partial V}{\partial S}+\frac{1}{2}\sigma^2S^2U_t\frac{\partial^2 V}{\partial S^2}-rV=0
\end{equation}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}          ==>>  [#]
%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%   \citet{key}         ==>>  Author [#]

%% References with bibTeX database:

\bibliographystyle{model1-num-names}
\bibliography{<your-bib-database>}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use model1-num-names.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}
